### 2013-09-18 Publications/2013-ISBI14/02-introduction.tex
Fixes (minor)

Even though aforementioned techniques for distortion correction
have been studied \cite{zeng_image_2002,wu_comparison_2008},
the lack of a gold-standard limit the possible benchmarking 
strategies. \cite{irfanoglu_effects_2012} opened the question
of the impact of the distortions on tractography. In this work,
we propose an evaluation framework using a detailed digital 
phantom designed for tractography. Using this framework,
we are able to compare several correction techniques and we
provide results related to their performance in the task
itself and their impact on subsequent tractography.

>>>>

Even though aforementioned techniques for distortion correction
have been studied \cite{zeng_image_2002,wu_comparison_2008},
the lack of a gold-standard limits the possible benchmarking 
strategies. \cite{irfanoglu_effects_2012} opened the question
of the impact of the distortions on tractography. In this work,
we propose an evaluation framework using a detailed digital 
phantom designed for tractography. Using this framework,
we are able to compare several correction techniques and we
provide results related to their performance in the task
itself and their impact on subsequent tractography.
